\documentclass{letter}
%\usepackage{geometry}






\begin{document}
Dear Application Commitee, \par
My motivation for this program stems from my desire to build a life in Germany. Having a solid intermediate level German will have a great positive effect on both my professional and personal life. With an intermediate level of German, I will have a wider selection of professional and academic opportunities in Germany, both during and after my graduation. I also want to gain as much experience as I can during my studies, hence reaching the level B1 at the end of my first semester will be an important milestone.\\\\
My aim is  to continue my career in a tech company in Munich and to  have at least B2 level of German knowledge after finishing my education. Because of this I have already completed A2 level to have a base before starting my studies in TUM. I believe completing German matters program will help me a lot while building up my career path.\\\\
During my undergraduate studies my motivation was to learn as much as possible and improving my abilities in many different aspects of Computer Science. Hence I always focused on participating in research projects while maintaining a successful GPA, as a result of these I had really busy and challenging schedule and quite the heavy workload. My motivation and dedication helped me to overcome all these obstacles to reach my targets during my studies. \\\\
I believe German matters program is a perfect opportunity for me to improve my German since it is embedded to the school curriculum which makes it easier for me to attend during the lecture period. For my first semester, I will take 30 credits, 4 courses, which is the recommended amount of workload and I will not work part time during this semester. Therefore I will have the time to dedicate myself to the program and I am confident that I can manage my time for both my courses and for German matters.
\\\\Kind Regards,
\par Kerem Yildirir

\end{document}